### 2025-12-18 CV2/talks.tex
-

>>>>

  \item {\bf Talk: Recent Advances in Adaptive Convex Optimization}, \href{https://www.mathnet.ru/eng/conf2402}{\em Mathematical Foundations of Artificial Intelligence Seminar}, Steklov Mathematical Institute, Moscow, Russia (November 2025)
  \item {\bf Talk: Understanding Gradient Orthogonalization for Deep Learning via Non-Euclidean Trust-Region Optimization}, \href{https://cs.hse.ru/en/iai/hdilab/seminar/}{\em HDI Lab Structural Learning Seminar}, Higher School of Economics, Moscow, Russia (December 2025)
